---
title: "R Notebook"
output: html_notebook
---

# Understanding Marginal probability

```{r echo=TRUE}
# Createv a Matrix with random variables that represents our event space
set.seed(123)
event.space <- rnorm(16, 6, 2) %>% 
  floor() %>% 
  matrix(nrow = 4, ncol = 4)

# Ensure that probability sums to 1
total <- (event.space %>% sum())
event.space <-
event.space / total

# View event space
event.space %>% round(2)
```

Let's say that the rows represent all possible outfits one could wear (We'll call this the outfit event) and the columns represent all possible weather types (We'll call this the weather event). We'll name the possible outcomes for outfits as {`r rownames(event.space)`} and the possible outcomes for weather as {`r colnames(event.space) `}
```{r}
# Name the outcomes
rownames(event.space) <- c("Heavy Coat", "Tshirt", "Swimsuit", "Raincoat")
colnames(event.space) <- c("Snow", "Rainy", "Sunny", "Windy")
event.space %>% round(2)
```

The Marginal probabilitiy of event A = D is simply the sum of all the occurences of D for a each possible value of Event 2

```{r}
(marginal.prob.of.d <- sum(event.space["D", ]))
```

What we've done is taken the sum of the joint probabilities where Event 1 is D and Event 2 is all possible values. Written explicitly, this becomes
\[
P(D,I) + P(D,J)+P(D,K)+P(D,L)+P(D,M)
\]\
And in code:
```{r}
(marginal.prob.of.d <- event.space["D","I"] + event.space["D","J"] +
   event.space["D","K"] + event.space["D","L"] + event.space["D","M"])
```

This is important to know because sometimes we know joint probabilities but want to express (i.e. - what's the probability of one wearing a heavy coat?)

# Joint Probability

We mentioned earlier the concept of joint probability. Essentially, this is the probability of both a specific weather and outfit event occuring (i.e. - what's the probability of wearing a rain coat AND that it's raining)
```{r}
(joint.probability <- event.space["Raincoat", "Rainy"])
```

