---
title: "R Notebook"
output: html_notebook
---

# Understanding Marginal probability

```{r echo=TRUE}
# Createv a Matrix with random variables that represents our event space
set.seed(123)
event.space <- rnorm(25, 6, 2) %>% 
  floor() %>% 
  matrix(nrow = 5, ncol = 5)

# Ensure that probability sums to 1
total <- (event.space %>% sum())
event.space <-
event.space / total

# View event space
event.space %>% round(2)
```

Let's say that the rows represent all possible outcomes of Event 1 and the columns represent all possible outcomes of Event 2. To make things easier, we'll name the possible outcomes for event A as {`r LETTERS[4:8]`} and the possible outcomes for event B as {`r LETTERS[9:13]`}
```{r}
# Name the outcomes
rownames(event.space) <- c(LETTERS[4:8])
colnames(event.space) <- c(LETTERS[9:13])
event.space %>% round(2)
```

The Marginal probabilitiy of event A = D is simply the sum of all the occurences of D for a each possible value of Event 2

```{r}
(marginal.prob.of.d <- sum(event.space["D", ]))
```

What we've done is taken the sum of the joint probabilities where Event 1 is D and Event 2 is all possible values. Written explicitly, this becomes
\[
P(D,I) + P(D,J)+P(D,K)+P(D,L)+P(D,M)
\]\
And in code:
```{r}
(marginal.prob.of.d <- event.space["D","I"] + event.space["D","J"] +
   event.space["D","K"] + event.space["D","L"] + event.space["D","M"])
```

This is important to know because sometimes we know joint probabilities but want to express 
